Motivating Letter for Submission: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2021-11-18 cover_letter/cover_letter.Rmd
re-structure reproducibility folder, check point 1

---
title: "cover_letter"
author: "xxx"
date: "10/13/2021"
output: html_document
---

## Cover Letter

@@

>>>>

---
title: "Motivating Letter for Submission: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets"
author: "Wangqian Ju and Heike Hofmann"
date: "10/13/2021"
output:
  pdf_document: default
  html_document: default
---

@@

Below is an explanation of non-standard files/folders included with the submission.

+   **data** folder: contains data to demonstrate the cmpsR package and reproduce various results in the paper. 
+   **reproducible** folder: contains R scripts and data necessary to reproduce all aspects of this submission.
+   **ju-hofmann_files/figure-latex** folder: contains figures and plots used in the paper
